Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-07-15 analysis/paper/sim_survey_paper.Rmd
Draft "fan plots" for paper

|          Correlation across ages in spatial distribution |       $\varphi_{\xi, age}$ |           0.1* |

@@

d <- merge(sim$surveys, sim$age_strat_error, by = "survey")
d <- d[d$sim %in% 1:1000 & d$year == which_year & d$set_den %in% which_set_dens &
         d$lengths_cap %in% which_len_caps & d$ages_cap == 10, ]
d$age[d$age > 8] <- 8 # aggregate beyond 8
d <- d[, list(I_hat = sum(I_hat), I = sum(I)), 
       by = c("year", "age", "sim", "survey", "set_den", "lengths_cap")]

p <- ggplot(data = d) + 
  geom_line(aes(x = age, y = I_hat, color = sim, group = sim), size = 0.1) +
  geom_line(aes(x = age, y = I), color = viridis::viridis(1), size = 0.5) +
  scale_color_viridis(begin = 0.5, guide = FALSE) +
  facet_grid(set_den ~ lengths_cap) +
  xlab("Age") + ylab("Abundance index") +
  theme_minimal() +
  scale_y_continuous(labels = format_si()) +
  scale_x_continuous(expand = c(0.01, 0), 
                     labels = c("2", "4", "6", "8+"), 
                     breaks = seq(2, 8 , 2)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm"))

@@

which_set_dens <- c(0.0005, 0.002, 0.01)
which_len_caps <- c(10, 100, 1000)
which_age <- 4

d <- merge(sim$surveys, sim$age_strat_error, by = "survey")
d <- d[d$sim %in% 1:1000 & d$age == which_age & d$set_den %in% which_set_dens &
         d$lengths_cap %in% which_len_caps & d$ages_cap == 10, ]

p <- ggplot(data = d) + 
  geom_line(aes(x = year, y = I_hat, color = sim, group = sim), size = 0.1) +
  geom_line(aes(x = year, y = I), color = viridis::viridis(1), size = 0.5) +
  scale_color_viridis(begin = 0.5, guide = FALSE) +
  facet_grid(set_den ~ lengths_cap) +
  xlab("Year") + ylab("Abundance index") +
  theme_minimal() +
  scale_y_continuous(labels = format_si()) +
  scale_x_continuous(expand = c(0.01, 0)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm"))

@@

>>>>

|          Correlation across ages in spatial distribution |       $\varphi_{\xi, age}$ |           0.5* |

@@

d <- merge(sim$surveys, sim$age_strat_error, by = "survey")
d <- d[d$year == which_year & d$set_den %in% which_set_dens &
         d$lengths_cap %in% which_len_caps & d$ages_cap == 10, ]
d$age[d$age > 8] <- 8 # aggregate beyond 8
d <- d[, list(I_hat = sum(I_hat), I = sum(I)), 
       by = c("year", "age", "sim", "survey", "set_den", "lengths_cap")]

## quantiles for fan plot
quants <- seq(90, 10, by = -10)
ints <- lapply(quants, function(q) {
  d[, list(prob = paste0(q, "%"),
           lower = quantile(I_hat, prob = (1 - q / 100) / 2),
           upper = quantile(I_hat, prob = 1 - (1 - q / 100) / 2)), 
    by = c("year", "age", "set_den", "lengths_cap")]
})
ints <- rbindlist(ints)
ints$prob <- factor(ints$prob, levels = paste0(quants, "%"))

true <- d[d$sim == 1, ]

cols <- viridis::viridis(3)
ggplot(data = ints) + 
  geom_ribbon(aes(x = age, ymin = lower, ymax = upper, fill = prob, alpha = prob)) +
  geom_line(aes(x = age, y = I), data = d, color = cols[1], size = 1) +
  scale_fill_viridis(name = "Pr", discrete = TRUE, begin = 0.1) +
  scale_alpha_discrete(name = "Pr") + 
  facet_grid(set_den ~ lengths_cap) +
  xlab("Age") + ylab("Abundance index") +
  theme_minimal() +
  scale_y_continuous(labels = format_si()) +
  scale_x_continuous(expand = c(0.01, 0), 
                     labels = c("2", "4", "6", "8+"), 
                     breaks = seq(2, 8 , 2)) +
  guides(color = guide_legend(keywidth = 0.4, keyheight = 0.25, 
                              default.unit = "cm", ncol = 1)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm"))

@@

which_set_dens <- c(0.0005, 0.002, 0.01)
which_len_caps <- c(10, 100, 1000)
which_age <- 6

d <- merge(sim$surveys, sim$age_strat_error, by = "survey")
d <- d[d$age == which_age & d$set_den %in% which_set_dens &
       d$lengths_cap %in% which_len_caps & d$ages_cap == 10, ]

## quantiles for fan plot
quants <- seq(90, 10, by = -10)
ints <- lapply(quants, function(q) {
  d[, list(prob = paste0(q, "%"),
           lower = quantile(I_hat, prob = (1 - q / 100) / 2),
           upper = quantile(I_hat, prob = 1 - (1 - q / 100) / 2)), 
    by = c("year", "age", "set_den", "lengths_cap")]
})
ints <- rbindlist(ints)
ints$prob <- factor(ints$prob, levels = paste0(quants, "%"))

true <- d[d$sim == 1, ]

cols <- viridis::viridis(3)
ggplot(data = ints) + 
  geom_ribbon(aes(x = year, ymin = lower, ymax = upper, fill = prob, alpha = prob)) +
  geom_line(aes(x = year, y = I), data = d, color = cols[1], size = 1) +
  scale_fill_viridis(name = "Pr", discrete = TRUE, begin = 0.1) +
  scale_alpha_discrete(name = "Pr") + 
  facet_grid(set_den ~ lengths_cap) +
  xlab("Year") + ylab("Abundance index") +
  theme_minimal() +
  scale_y_continuous(labels = format_si()) +
  scale_x_continuous(expand = c(0.01, 0)) +
  guides(color = guide_legend(keywidth = 0.4, keyheight = 0.25, 
                              default.unit = "cm", ncol = 1)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm"))

@@

## Figure to-dos

- Fix facet labels (make them look like the wireframe plot)
- Add RMSE label to colorkey in wireframe plot
- Change vis_sim estimates plot to fan plots like used here
